Multifidelity Approximate Bayesian Computation with Sequential Monte Carlo Parameter Sampling\thanks{ Submitted to the editors January 2020 \funding{ This work is supported by BBSRC through grant BB/R000816/1.}}

### 2020-01-28 paper/shared.tex
Fix arxiv refs and subject codes and figures

\PassOptionsToPackage{demo}{graphicx}
\usepackage{amssymb, amsmath}
\usepackage{algorithmic}
\usepackage{cleveref}
\usepackage[demo]{graphicx}
\usepackage[caption=false]{subfig}

@@

\author{
Thomas P. Prescott\thanks{Mathematical Institute, University of Oxford, Woodstock Road, Oxford, OX2 6GG, UK (\email{prescott@maths.ox.ac.uk, ruth.baker@maths.ox.ac.uk})\funding{REB is supported by.}}
\and Ruth E. Baker\footnotemark[2]
}

>>>>

\usepackage{amssymb, amsmath}
\usepackage{algorithmic}
\usepackage{cleveref}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}

@@

\author{
Thomas P. Prescott\thanks{Mathematical Institute, University of Oxford, Woodstock Road, Oxford, OX2 6GG, UK (\email{prescott@maths.ox.ac.uk, ruth.baker@maths.ox.ac.uk})\funding{REB is supported by a Royal Society Wolfson Research Merit
Award and a Leverhulme Research Fellowship.}}
\and Ruth E. Baker\footnotemark[2]
}
